---
title: "updating-geometry-files"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{updating-geometry-files}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(localcovid19now)
```

Updating the geometry files for `localcovid19now` is important for when a country changes its borders, a better resolution file is available, a new country is being added to the package, and to correct existing errors.

Currently, updating country geometries is only intended to be done in interactive mode. This tutorial assumes use of a "Project" in RStudio, while it may be doable outside this environment. The process requires loading `devtools`.

1. Open a Project in RStudio, preferably a git-enabled project connected to the localcovid19now github repo or a fork.

2. Write a "process script" for the countries you want to update/add to the package. This can be done through either manually writing a new script or using the included "snippet."

    a. (Optional) Install the snippet.
    
        Open `geomTemplate.snippets` and copy the contents. In RStudio, go to Tools > Global Options > Code > Edit Snippets. Paste the contents of `geomTemplate.snippets` to the bottom of the "edit snippets" page. Make sure all indents are done using "tab" (they will automatically be highlighted red if not).

    b. Open a new script and type `geomTemplate` and then "shift+tab" if it did not autocomplete. If you did not install the snippet, use a previous example from `tools/processed`.

    c. Fill in the blanks. While you may run the code to make sure it works, you should not save any outputs.
  
        i. Use the `m49` data set from the package to check if the country names match in the reference data set.

    d. Save the file as `tools/toProcess/process[CountryName].R` using lower camel case.

3. Run `library(localcovid19now); library(devtools)`.

    a. If you have not already installed the package, use the "install and restart" option in RStudio's "Build" menu.

4. Run `updateGlobal()`. This function will add the new geometries to the existing ones and save all changed geometries to the `data` folder for use in `Load[Country]` functions.

Make sure that the `Load[Country]` function for the new countries uses the correct column names in the newly-created geometry files. 
